### 2018-04-18 paper.Rmd
testing density plots

The data imported into childes-db is subject to data integrity checks to ensure that our import of the corpora is accurate and preferable over ad-hoc parsers developed by many individual researchers.
<!-- MCF: more testing details would be useful -->
In order to evaluate our success in replicating CLAN parses, we compared unigram counts in our database with those outputted by CLAN, the command-line tool built specifically for analysis of transcripts coded in CHAT.
In particular, the CLAN commands FREQ and MLU were used to compare total token counts and mean lengths of utterance for every speaker in every transcript; these numbers were compared to our own using the Pearson correlation coefficient. 
The results of the comparison were .99 and .98 for the unigram count and mlu data, respectively, indicating a reliable parse on our end.
<!-- SM: what were the results of these comparisons?  -->
<!-- AS: technically this is all we do right now SM: what more can we do for low technical investment-->

@@

<!-- AS: not sure whether I should have included this; I didn't want to overwhelm the reader -->
<!-- SM: need a few more details: what kind of model was it basically? loess, logistic growth curve, etc. -->

@@

```{r echo=TRUE, warning=FALSE}
ggplot(data, aes(x = age_years, y = measure, 
                 color = target_child_sex)) +
  geom_point(alpha = .3) + 
  geom_line(data = mod_data, 
            aes(x = age_years, y = measure, color = target_child_sex)) +
  facet_wrap(~language) + 
  ggthemes::theme_few() + 
  ggthemes::scale_color_ptol(name = "Sex") + 
  xlim(0,max_age) + 
  ylim(0,15) + 
  xlab("Age (years)") + 
  ylab("MTLD") + 
  theme(legend.position = "bottom")
```

This plot reveals a slight gender difference in linguistic productivity in young children, replicating the moderate female advantage found by @eriksson2012differences.
The goal of this analysis was to showcase an example of the the steps involved in using `childesr` for exploring the CHILDES dataset, as well as some of the potential hazards -- sparsity and non-independance-- that emerge in working with a diverse set of corpora, many of which are longitudinal.

>>>>

The data imported into childes-db is subject to data integrity checks to ensure that our import of the corpora is accurate and preferable over ad-hoc parsers developed by many individual researchers.
<!-- MCF: more testing details would be useful -->
In order to evaluate our success in replicating CLAN parses, we compared unigram counts in our database with those outputted by CLAN, the command-line tool built specifically for analysis of transcripts coded in CHAT.
In particular, the CLAN commands FREQ and MLU were used to compare total token counts and mean lengths of utterance for every speaker in every transcript; these numbers were compared to our own using the Pearson correlation coefficient. 
The results of the comparison were .99 and .98 for the unigram count and mlu data, respectively, indicating a reliable parse on our end.

```{r}
# plot error between clan counts and our counts for speaker unigrams
freq_data <- read_csv("data/freq_testing.csv")

ggplot(freq_data %>%
         mutate(error = abs(clan - db) / clan), 
       aes(error)) +
  geom_density() +
  xlim(0,.25)
```

```{r}
# plot error between clan counts and our counts for mlu-w
mlu_data <- read_csv("data/mlu_testing.csv")

ggplot(freq_data %>%
         mutate(error = abs(clan - db) / clan), 
       aes(error)) +
  geom_density() +
  xlim(0,.25)
```

<!-- SM: what were the results of these comparisons?  -->
<!-- AS: technically this is all we do right now SM: what more can we do for low technical investment-->

@@

@@

```{r echo=TRUE, warning=FALSE}
ggplot(data, aes(x = age_years, y = measure, 
                 color = target_child_sex)) +
  geom_point(alpha = .3) + 
  geom_line(data = mod_data, 
            aes(x = age_years, y = measure, color = target_child_sex)) +
  facet_wrap(~language) + 
  ggthemes::theme_few() + 
  ggthemes::scale_color_ptol(name = "Sex") + 
  xlim(0,max_age) + 
  ylim(0,15) + 
  xlab("Age (years)") + 
  ylab("MTLD") + 
  theme(legend.position = "bottom")
```
This plot reveals a slight gender difference in linguistic productivity in young children, replicating the moderate female advantage found by @eriksson2012differences.
The goal of this analysis was to showcase an example of the the steps involved in using `childesr` for exploring the CHILDES dataset, as well as some of the potential hazards -- sparsity and non-independance-- that emerge in working with a diverse set of corpora, many of which were collected in longitudinal studies.
